### 2024-03-28 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendere

Some patterns are noticible. In future explorations, we should hope to reach
some interpretations and hopefully discuss them with local friends who
know something about this area.

>>>>

Some patterns are noticible. In future explorations, we should hope to reach
some interpretations regarding repeating movement in certain hours,
such as the end of the work day, in relation to certain destinations,
like major train stations.
We sould certainly hope to discuss them with local friends who
know something about this area.
